Conformance Checking Using Embeddings and it's Applicability in the Internet of Things

### 2021-12-20 paper.tex
reproducibility

\subsubsection{Quality criteria}
It is important to note that model quality is not a single-dimensional criterion, instead, it exists in a multi-dimensional space where the different axes represent different quality criteria.
As such it is not really appropriate to talk about one conformance metric, but instead, the four major axes should be considered.
\begin{enumerate}
	\item Fitness (few false negatives): The first of these metrics is fitness. This quality criterion is closely related to the statistical measure of recall. In the case of business process management fitness measures how many of the observed traces are actually possible executions of the model.
	\item Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives. In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
	\item Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility.
	\item Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
	It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model. However, that would not be a model that generalizes well since it captures none of the dynamism of the underlying process. 
	This is the most difficult criterion since it is arguing about unknown possible future behavior.
\end{enumerate}

Of these four quality criteria conformance checking is mainly concerned with precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.

@@

\todo{formula}

@@

\color{black}
\section{Discussion}
\label{sec:discussion}
\subsection{Future Work}
Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation were the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.

>>>>

%\subsubsection{Quality criteria}
%It is important to note that model quality is not a single-dimensional criterion, instead, it exists in a multi-dimensional space where the different axes represent different quality criteria.
%As such it is not really appropriate to talk about one conformance metric, but instead, the four major axes should be considered.
%\begin{enumerate}
%	\item Fitness (few false negatives): The first of these metrics is fitness. This quality criterion is closely related to the statistical measure of recall. In the case of business process management fitness measures how many of the observed traces are actually possible executions of the model.
%	\item Precision (few false positives): Closely related to the statistical measure of precision, this metric measures how many false positives there are in relation to true positives. In the case of process models, this is the fraction of traces allowed by the model that are actually observed in the log.
%	\item Simplicity: How "simple" a model is, generally a smaller model that describes a process equally well is preferred for reasons such as performance and comprehensibility.
%	\item Generalization: Generalization is the model's ability to be applicable to possible future traces of a given process. 
%	It would clearly be possible to create a model with perfect precision and recall, by simply encoding the traces themselves in the model. However, that would not be a model that generalizes well since it captures none of the dynamism of the underlying process. 
%	This is the most difficult criterion since it is arguing about unknown possible future behavior.
%\end{enumerate}
%
%Of these four quality criteria conformance checking is mainly concerned with precision and recall, but depending on the algorithms possibly some statements about generalization could be made as well.

@@

@@

\subsection{Reproduction of Experiments}
The authors published some \href{https://github.com/jaripeeperkorn/Conformance-checking-using-activity-and-trace-embeddings}{source code} accompanying the paper.
To verify their results as well possibly perform some additional experiments it seemed appropriate to look at said code and try to reproduce their results as good as possible.
After some initial technical difficulties, since very specific package versions were needed, their code was successfully run.
They provide three separate Python scripts for their implementations of the  WMD,ICT and \emph{trace2vec} methods.

Aside from that they also provide Jupyter notebooks for their experiments, however sadly these do not run the whole experiment, instead they only perform the experiment for one parameter combination.
To reproduce their noise experiment it is thus necessary to manually run the corresponding notebook twelve times, once for each parameter combination, manually note down the results of each run and merge them manually at the end.
This was deemed to be out of scope for this paper.
Additionally, the discovery experiment only determined fitness and precision of the WMD, ICT and \emph{trace2vec} methods and not the reference methods, so it is unclear at this point how the fitness and precision values for the reference methods were determined.
Overall it can be said that the results from the paper are at least partially reproducible, and the provided implementation gives good pointer into how the methods were set up in detail, but running the experiments and collecting the results requires more effort than should be necessary.

Lastly, it was considered to design and run another experiment here to evaluate performance and scaling differences between the embedding based approaches and reference approaches like alignments, behavioral fitness and ETC precision, as this is one of the main selling point especially in the IoT and the authors sadly did not include an experiment to that effect.
In light of the complications with the existing experiments and the fact that no evaluation of the reference metrics was included in their code this idea was deemed out of scope for this paper.
\color{black}
\section{Discussion}
\label{sec:discussion}
\subsection{Future Work}
Peeperkorn et al. obtained promising first results for a novel embedding-based approach towards conformance checking.
Yet as the focus was mainly on the introduction and development of a prototype for such an approach there are some natural limitations.
Arguably the biggest limitation were the logs used for the experimental validation.
All used logs were completely synthetic, generated from random process trees.
It is unclear how well the 12 trees used for this resemble real processes and whether these tree configurations are sufficiently representative for the variation exhibited in real life trees\footnote{12 tree configurations were used, 3 sizes and 4 different probability distributions for operations, how strong these vary should be investigated}.
As such it should be a priority to test the proposed methods on real logs, possibly popular benchmark cases, and also to systematically broaden the parameters for random process tree generation to cover more different classes.
